Price of Anarchy for Mean Field Games

### 2018-07-16 PoA.tex
finished with proposition 5

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t &= \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, for $t \in [0,T)$, we have:
	\begin{equation*}
	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
	Similarly, we can show that for $t \in [0,T)$:
	$$\lim_{\bar{b}_2 \to \infty} (b_2 + \bar{b}_2) w^{\bar{b}_2}_t = \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},$$
	Hence, by the bounded convergence theorem (ToDo: show all 3 terms are uniformly bounded), we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$	
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
\end{proof}

>>>>

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, for $t \in [0,T)$, we have:
	\begin{equation*}
	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
	Similarly, we can show that for $t \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}.
	\end{split}
	\end{equation*}
	Similar to the proof of Proposition \ref{prop:r_bar_r}, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
	\begin{equation*}
	\begin{split}
	|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
	|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
	|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
	\end{split}
	\end{equation*}

	Hence, by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$	
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
\end{proof}
